Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-20 docs/paper/paper.Rmd
some more planning detail

@@

As well as posterior predictions and forecasts for notifcations  the model also return several epidemiological summary statistics which may be useful for drawing inferences about underlying transmission dynamics. These are the log scale growth rate ($g^{o, \delta}_t$), and the instantaneous effective reproduction number ($R^{o, \delta}_t$). These are calculated as follows:

@@

@@

- Date range of forecasts
- Forecasts per country
- Summarises general trends in incidence in the data

>>>>

- Data from JHU as used as truth data by the ECDC forecasting hub.
  - When accessed
  - Aggregated to epiweek as in the ECDC forecasting GitHub
  - Countries included
  - Dates of data included
- Forecasts from the ECDC forecast hub
  - Forecasts dowloaded for the model proposed here and the ECDC ensemble
  - Forecast format
  - Forecases from when and horizon
  - Ensemble construction and reference

@@

As well as posterior predictions and forecasts for notifcations the model also returns several epidemiological summary statistics which may be useful for drawing inferences about underlying transmission dynamics. These are the log scale growth rate ($g^{o, \delta}_t$), and the instantaneous effective reproduction number ($R^{o, \delta}_t$). These are calculated as follows:

@@

- Visualise forecasts across time horizons in examplar countries.
- Weighted interval score.
- Calibration and coverage.
- Relative interval score.
- Relative interval score overall, distribution of scores, by horizon both overall and distribution, by location overall and distribution.
- Relative interval score by interval range by horizon
- Calibration at 50 and 90 credible intervals
- Coverage across intervals.

@@

- Date range of forecasts
- Forecasts per country
- Total number of forecast models and average per location and per forecast date
- Summarises general trends in incidence in the data
